Efficiently summarising relationships in large samples: a general duality between statistics of genealogies and genomes

### 2019-09-06 treestats_paper.tex
h(p) should be f(p) as it is written later in Example 2?

Many population genetic summary statistics can be defined using the allele frequency spectrum
of a collection of homologous sequences.
Concretely, write $p_i(a)$ for the frequency of allele $a$ at a site $i$,
and $h(p)$ for the allele frequency spectrum
-- i.e., the number of alleles whose frequency is $p$ in our sample --
and suppose that for some function $f()$, we want to compute $\sum_p h(p) f(p)$.
(For instance, mean genetic diversity is computed with $h(p) = p (1-p)$.)
Since this is a simple sum over sites,
we can compute this by summing over the $L$ loci, as
\begin{align*}
    \sum_p h(p) f(p) = \sum_{i=1}^L \sum_a f(p_i(a)).
\end{align*}
(Note that since the ancestral allele is included, this is a function of the
is invariant to relabeling of alleles.)
If we know where each mutation has occurred on the genealogy,
we can easily find the frequency of the corresponding allele by counting how many samples
occur below that mutation in the tree (and accounting for those that subsequently mutate).

>>>>

Many population genetic summary statistics can be defined using the allele frequency spectrum
of a collection of homologous sequences.
Concretely, write $p_i(a)$ for the frequency of allele $a$ at a site $i$,
and $h(p)$ for the allele frequency spectrum
-- i.e., the number of alleles whose frequency is $p$ in our sample --
and suppose that for some function $f()$, we want to compute $\sum_p h(p) f(p)$.
(For instance, mean genetic diversity is computed with $f(p) = p (1-p)$.)
Since this is a simple sum over sites,
we can compute this by summing over the $L$ loci, as
\begin{align*}
    \sum_p h(p) f(p) = \sum_{i=1}^L \sum_a f(p_i(a)).
\end{align*}
(Note that since the ancestral allele is included, this is a function of the
is invariant to relabeling of alleles.)
If we know where each mutation has occurred on the genealogy,
we can easily find the frequency of the corresponding allele by counting how many samples
occur below that mutation in the tree (and accounting for those that subsequently mutate).
